\chapter{Characters}
When you create your character you should think about, that (s)he makes for a living, what have happened to (s)he earlier in life, that makes the person to what (s)he is today.
Your character can be swordsman, a servant, a history teller, a priest, a monk or nun, an thief, a local witch or everything you want.
The character should be prepared in some way or another to go on an adventure, work together with other characters and in someway help another being.
This will ensure the start of the campaign and for you to make the most fun out of the game.
\\\\
When you are making an character you will get 30 Gp, or another GM provided amount, to "buy" stuff for, this is money you character in his/her life in some way or another gathered.
Maybe some of it is made by him/her, inherited, or saved up for to buy.

\section{Exploits}
We have defined some exploit for you to use, if you want your character to use magic.
Only special kind of people can use magic, and this is ensured by the the exploits.
A character without the exploit to become a priest cannot use the magic ability provided from God.
The story behind who and why the character wanted to be connected to God in that way is up to you and the Game Master.
This rule apply to the exploit for Witch/Sorcerer as well.

\begin{itemize}
    \item The ability to become a priest, and use the magic ability of a priest.
    \item The ability to become a Witch/Sorcerer and use the magic ability of a Witch/Sorcerer.
\end{itemize}
