\chapter{Magic}
Magic in the Medieval period is nearly non existing.
But priest can by the power of God, make magical things happen like, heal a wounded person, or make a fighter stronger, to win the battle with the creature invading the kingdom.
A priest can also punish you by the name of God.

Priest uses the power of God to make magic happens, but witches and sorcerers do not gets their powers from God, but by studying nature and uses herbs, to make the wound heal, or to cure the sickness.
Most witches and sorcerers are hunted by the towns people, because people think the witches and sorcerers are evil, or are up to harm.
That is why many witches and sorcerers hides in the wood or away from others.
But those witches and sorcerers who manage to prove them self trustworthy to the town or even the king, may have a better life.


The difficulty is used when you are performing the spell and make a skill roll, you add the difficulty to the roll, and then sees if you success the magic skill check.
\section{Priests}
\magic{Prayer}{0}{2}{By a prayer to God you heal a wounded person by 1 HP over the next hour.}

\magic{Blessing}{1}{5}{By a blessing from God you you strengthen a person by +1 $Agi$ up to 1 hour.}

\magic{The Curse of God}{1}{8}{By the will of God you can curse a victim. The victim will have -2 on $Agi$ up to 2 hours}


\section{Witches and Sorcerers}
\magic{Healing by Herbs}{0}{2}{By the use of herbs and a little magic you heal a wounded person by 1 HP over the next hour}

\magic{Cursed Blood}{1}{5}{By a lure of the victims hair, you can with a boiling pot and a little magic, curse the victim. The victim get -1 $Con$ up to 1 hour.}

\magic{The Ritual of the beast}{1}{8}{By performing a ritual over a person, by using the burning hair of a bull. The person get +1 $Str$ and +1 $Con$ up to 2 hours}