\chapter{Setting}
The medieval time period, is a period were the church and kings rules.
Everyone tries to survive day after day, and make the presence be as tolerable as possible.

The medieval period starts at the fall of the roman empire. \footnote{https://en.wikipedia.org/wiki/Middle\_Ages}
Some of the culture from the roman empire may have survived, or even shaped the medieval period, from place to place.

\subsection{Currency}
Moneys is used to trade in the medieval time period. The money to use is, cobber pieces Cp, silver pieces Sp, and gold pieces Gp. 10 cobber pieces is worth 1 silver piece, and 10 silver pieces is worth 1 gold piece.

How much is a cobber piece worth, what can you buy with it, and how much do a usually people make.

A normally day labour, is payed around 5 Cp, from which he can buy a meal at the in for 2 Cp, and a mug of ale for 1 Cp, so he earns 2 Cp which he can save, to buy something bigger.
A room at the local inn would cost around 2 Sp pr. night.

\section{Religion}
The Christianity and the believe in God have great power in the medieval period.
The church make people believe that if they sin they are going to hell, and that way make people pay to the get relive from God, through the church.

\section{Rulers}
Typical in the medieval time period there was kings and queens to rule over bigger areas of land.
But the king or queen could not be every were, so there was typical some represents for the ruler in smaller parts of the kingdom.
These represent was typical in the bigger city's and was travelling around to collect taxes for the king.
The rules of the kingdom was typical fairly simple, do not steal, do not kill, pay you taxes, or so on.
Bigger towns could have some kind of judge, or the towns people could make a public vote, to determined the thief punishment.
Should the thief gets his hand cut of, or just a finger, or should he sit in the pillory for some time.
